\documentclass[12pt,a4paper,sans]{moderncv}

% Set style and color
\moderncvstyle{casual} % or 'classic', 'banking', etc.
\moderncvcolor{black}

% Encoding and language
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% Use XeLaTeX or LuaLaTeX to load fonts with fontspec
\usepackage{fontspec}
\setmainfont[
  Path=/home/crnvl96/.local/share/fonts/Roboto/,
  UprightFont = *-Regular.ttf,
  BoldFont = *-Bold.ttf,
  ItalicFont = *-Italic.ttf,
  BoldItalicFont = *-BoldItalic.ttf
]{Roboto}

\usepackage[scale=0.8]{geometry}

% Personal Information
\name{Adran}{Carnavale}
\address{66040105 Belém - PA}{}{}
\phone[mobile]{+55 16993610234}
\email{adran.carnavale@gmail.com}
\social[linkedin]{adrancarnavale}
\social[github]{crnvl96}
\homepage{crnvl96.dev}

\begin{document}

%----- LETTER SETUP -----%
\recipient{Hiring Manager}{***}
\date{25 June 2024}
\opening{Dear Hiring Manager,}
\closing{Sincerely}
\makelettertitle

I was excited to hear of this job opportunity from my ***,
***, who thought I would be a good match for this position.
With a background in both technology and military education, I bring
a unique blend of technical expertise and disciplined work ethic that
aligns with your requirements.

At Serena Energy, I have developed and maintained a large-scale
client registration system supporting over 4,000 clients. My
experience includes backend technologies like Node.js, Docker, and
PostgreSQL, as well as frontend technologies like React and Vite.js.
I work daily with AWS to ensure robust cloud infrastructure and
perform integrations with external APIs, including Oracle.

My education at EFOMM provided a strong foundation in hierarchy,
teamwork, resilience, responsibility, and adaptability. At Trybe, I
earned certifications in Introduction to Computer Science, Front-End
Development, Back-End Development, and Computer Science Foundations.
I also worked as a student instructor, enhancing my communication and
teaching abilities.

I am passionate about contributing to open-source projects,
particularly within the Neovim community. My hobbies include board
games and sports, which contribute to my strategic thinking and teamwork skills.

I am confident that my background and experience would be an asset to
***. Thank you for considering my application. I look forward
to discussing how my skills align with your organization's goals.

\makeletterclosing

\end{document}
