\documentclass[12pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{black}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage{fontspec}
\usepackage[scale=0.8]{geometry}

\setmainfont[
  Path=/home/crnvl96/.local/share/fonts/Roboto/,
  UprightFont = *-Regular.ttf,
  BoldFont = *-Bold.ttf,
  ItalicFont = *-Italic.ttf,
  BoldItalicFont = *-BoldItalic.ttf
]{Roboto}

\setlength{\hintscolumnwidth}{2.5cm}
\setlist[itemize]{label=$\bullet$, topsep=0pt, parsep=0pt, partopsep=0pt}

% Personal Information
\name{Adran}{Carnavale}
\address{Belém - PA, 66040105, Brazil}{}{}
\phone[mobile]{+55 16993610234}
\email{adran.carnavale@gmail.com}
\social[linkedin]{adrancarnavale}
\social[github]{crnvl96}
\homepage{crnvl96.dev}

\begin{document}
\makecvtitle

%----- SUMMARY -----%
\section{Summary}
\cvitem{}{\small Hardworking and resourceful individual committed to
  building user-friendly, functional, and sustainable web applications.
  Highly skilled in project management and multitasking to deliver
complex projects within tight deadlines.}

%----- EXPERIENCE -----%
\section{Experience}
\cventry{\textit{07/2022 -- Current}}{Full Stack Developer}{Serena Energy}{São
Paulo, Brazil}{}{
  \begin{itemize}
    \item Develop and maintain a large-scale client registration and
      management system, supporting over 6,000 clients.
    \item Utilize backend technologies such as Node.js, Docker, and PostgreSQL.
    \item Employ frontend technologies, including React and Vite.js,
      to enhance the user interface.
    \item Perform integrations with external APIs, including Oracle.
    \item Work daily with AWS to deploy, manage, and scale
      applications, ensuring robust cloud infrastructure and high availability.
  \end{itemize}}

%----- SKILLS -----%
\section{Skills}
\cvitem{\textit{Frontend}}{React}
\cvitem{\textit{Backend}}{Node.js, Golang, Python, PostgreSQL, Docker}
\cvitem{\textit{Cloud}}{AWS}

%----- EDUCATION -----%
\section{Education}
\cventry{\textit{2022}}{Course- Web development}{Trybe}{São Paulo, SP}{}{
  \textbf{Achieved certifications:}
  \begin{itemize}
    \item Introduction to Computer Science
    \item Utilize backend technologies such as Node.js, Docker, and PostgreSQL.
    \item Front-end development
    \item Back-end development
    \item Computer science
  \end{itemize}
}

\cventry{\textit{2022}}{Internship - Student instructor}{Trybe}{São Paulo,
SP}{}{Assist students with
  tasks and projects.\\
  Enhanced problem-solving skills by guiding students through
  technical challenges.\\
  Developed communication and teaching abilities.
}

\cventry{\textit{2019}}{Diploma of Higher Education: Nautical
Sciences}{EFOMM}{Belém, PA}{}{}

%----- CERTIFICATIONS -----%
\section{Certifications}
\cvitem{}{\textbf{Golang expert}, by FullCycle Academy}
\cvitem{}{\textbf{CS50x}, by Harvard University}
\cvitem{}{\textbf{CS50p}, by Harvard University}

\end{document}
